\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-17 paper/mswp2012-proposal.tex
added 4. 3 of 5 questions

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Why is the project scientifically interesting?
\item Did others point out that this is an open question?
\item What are the innovative aspects that make it interesting?
\item How could the project break new ground scientifically?
\item To what extent are the objectives ambitious and beyond the state of the art (e.g. novel concepts and approaches or development across disciplines)?
\end{itemize}
}

>>>>

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Why is the project scientifically interesting?
\item Did others point out that this is an open question?
\item What are the innovative aspects that make it interesting?
\item How could the project break new ground scientifically?
\item To what extent are the objectives ambitious and beyond the state of the art (e.g. novel concepts and approaches or development across disciplines)?
\end{itemize}
}
\subsection{Scientifical point of view}

The approach to create a game out of tasks for sick people is not new. Dealing with traumatized children by example is nowadays often combined with a game. There are several different developments of games to fit the needs of different patients and problem fields. Furthermore there are very successful social gamifications like "Foursquare" \footnote{\url{https://foursquare.com/about/}} where people check in to places and earn achievements. All of that to keep track of what friends are doing. There is a high scientific potential in our idea because it combines many of already given approaches with existing infrastructure and organizations. For example a hospital can keep track of their patients health status after surgeries or treatments remote. A good idea would be to use the gathered data for better observation of diabetics. Hardware to gather the additional data is already available (see \footnote{\url{http://www.bgstar.com/web/ibgstar}}). These possibilities to collect data lead to more knowledge of different diseases and effectiveness of treatments. By example collection the data of stuff people eat and how much they do physical workouts combined with the actual disease can help creating specialized therapies and new approaches to improve existing ones.\\

\subsection{Open questions}
There are many studies about the influence of games in everyday life. Some scientists (see Jane McGonigal) are trying to use games to let people learn to get the most out of their lifes. Her experiments show that habits changed during playing a game with real world content like a global lack of oil are kept by most of the players even after ending the game. These experiments were made with small groups of 500 to 1700 people as a sort of proof of concept. No one knows what impact it may have when millions of people are achieving a healthier life through various gaming strategies and what comes out of the motivation they put into it. So many questions in the area of wide field gamification are still not answerable.

\subsection{Innovative apsects}
The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new. In Africa there is a project to do a basic doctor consultation by SMS. The reason for this is because nothing is spread that widely other than a simple mobile phone. Going many kilometers for a checkup to the next doctor is often way to far for people with no car or the possibility to use public transportation. Approaches like this one are already rolled out for certain diseases and specialized groups (see \footnote{\url{http://derstandard.at/1345166647163/Der-Doktor-im-iPhone}}). Combining all the existing programs to one big socialized game for healthier living could even change economy.
